Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Channel at the LHC with Multivariate Techniques

### 2015-11-27 paper/sec-pileup.tex
More work in the paper

>>>>

\subsection{Cut-flow}

The corresponding cut-flow tables in the case
of PU subtracted with SK, for $\la n_{\rm PU}\ra=80$,
are shown in Tables~\ref{tab:cutflow_SKPU80_1},
\ref{tab:cutflow_SKPU80_2} and~\ref{tab:cutflow_SKPU80_3},
for the total cross-sections, number of events expected and
signal significance at the HL-LHC, respectively.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
  \centering
  \scriptsize
  \input{tables/table_SKPU80_1.tex}
  $\,$ \\
  \vspace{0.5cm}
  \input{tables/table_SKPU80_2.tex}
  $\,$ \\
  \vspace{0.5cm}
    \input{tables/table_SKPU80_3.tex}
    \caption{\small
      Same as Table~\ref{tab:cutflow_noPU_1}, for the analysis
      including PU with $\la n_{\rm PU}\ra=80$ and SK substraction.
      \label{tab:cutflow_SKPU80_1}}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-11-27 paper/sec-results.tex
More work in the paper

\subsection{Cut flow and signal significance}

First of all we compare the cross-sections at various
analysis levels for the three categories, for signal and background events,
by providing a detailed cut-flow.
%
We consider all backgrounds enumerated in Sect.~\ref{mcgeneration},
then we discuss how results are modified if only the $4b$
component is kept.
%
we consider the following levels of the cut-flow
\begin{itemize}
\item {\bf C0}: cross-sections at the generator
  level, before any analysis cuts.
\item {\bf C1}:  cross-sections after the basic jet acceptance selection
  cuts, but before $b$-tagging.
\item {\bf C2}: cross-sections after after the $b$-tagging.
\end{itemize}
Note that {\bf C1} already includes the effect of the Higgs mass
window cut, Eq.~(\ref{higgsmasswindow}).
%
At the {\bf C0} level the numbers will be the same
for the three individual categories.

In the following, results are presented for the exclusive
categorisation defined in Sect.~\ref{sec:categorisation}.
%
%
At each stage of the cut flow, we also provide the number
of events that would be expected at the HL-LHC with
an integrated luminosity of $\mathcal{L}_{\rm int}
=3000$ fb$^{-1}$,
as well as 
the signal significance $S/\sqrt{B}$ and the signal
over background ratio $S/B$.
%
We emphasize that it is important not only to achieve a good signal
significance, $S/\sqrt{B}$, but also a good signal over background ratio $S/B$:
if the latter is too small, a very accurate
measurement of the background with an infeasible small
systematic uncertainty would be required.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
  \centering
  \begin{tabular}{c|c|c||c|c||c|c}
    \hline
    \multicolumn{7}{c}{Boosted category}\\
    \hline
    \hline
    &    \multicolumn{2}{c||}{$\sigma$ (fb)}   &  \multicolumn{2}{c||}{$N_{\rm ev}$}
    &   $S/\sqrt{B}$  & $S/B$\\
      &    Signal & Back   &  Signal  & Back
    &   & \\
    \hline
        {\bf C0}  &  36.9  & $9.9\,10^{9}$ & $1.1\,10^5$ & $3.0\,10^{13}$  &  0.020 & $3.7\,10^{-9}$\\
        {\bf C1}  &  0.46    & $1.3\,10^6$    &  $1.4\,10^3$   & $3.9\,10^9$     & 0.022     &  $3.5\,10^{-7}$ \\
        {\bf C2}  &  0.064     &  12.6     &  193   &  $3.8\,10^4$    &  0.99    &  $5.1\,10^{-3}$ \\
        \hline
  \end{tabular}
  $\,$\\
  \vspace{0.4cm}
  \begin{tabular}{c|c|c|c|c|c|c}
    \hline
    \multicolumn{7}{c}{Intermediate category}\\
    \hline
    \hline
    &    \multicolumn{2}{c|}{$\sigma$ (fb)}   &  \multicolumn{2}{c|}{$N_{\rm ev}$}
    &   $S/\sqrt{B}$  & $S/B$\\
      &    Signal & Back   &  Signal  & Back
    &   & \\
    \hline
         {\bf C0}  &  36.9  & $9.9\,10^{9}$ & $1.1\,10^5$ & $3.0\,10^{13}$  &  0.020 & $3.7\,10^{-9}$\\
        {\bf C1}  &   1.44    &   $1.1\,10^{7}$  &  $4.3\,10^3$   &  $3.3\,10^{10}$    &  0.024    &  $1.3\,10^{-7}$ \\
        {\bf C2}  &   0.22    &  722   &  660   &   $2.2\,10^6$   &   0.45   &  $3.1\,10^{-4}$ \\
        \hline
  \end{tabular}
  $\,$\\
  \vspace{0.4cm}
  \noindent
  \begin{tabular}{c|c|c|c|c|c|c}
    \hline
    \multicolumn{7}{c}{Resolved category}\\
    \hline
    \hline
    &    \multicolumn{2}{c|}{$\sigma$ (fb)}   &  \multicolumn{2}{c|}{$N_{\rm ev}$}
    &   $S/\sqrt{B}$  & $S/B$\\
      &    Signal & Back   &  Signal  & Back
    &   & \\
    \hline
       {\bf C0}  &  36.9  & $9.9\,10^{9}$ & $1.1\,10^5$ & $3.0\,10^{13}$  &  0.020 & $3.7\,10^{-9}$\\
        {\bf C1}  &   3.34    & $7.5\,10^{7}$    & $1.1\,10^4$    & $3.3\,10^{10}$     & 0.021     & $4.5\,10^{-8}$  \\
        {\bf C2}  &   0.54    &  $3.5\,10^{3}$   &  $1.6\,10^{3}$   &   $1.1\,10^{7}$   & 0.50     &  $1.5\,10^{-4}$ \\
        \hline
  \end{tabular}
  \caption{\small Cut-flow for the analysis of the boosted (top),
    intermediate (middle) and resolved (bottom)
    categories.
    %
    At each level of the cut-flow, we indicate the cross-sections and the number of
    expected events at the HL-LHC for $\mathcal{L}_{\rm int}=3$ ab$^{-1}$, both for
    signal events and for all the backgrounds combined.
    %
    We also provide in each case the
    signal significance $S/\sqrt{B}$ and the signal
    over background ratio $S/B$.
    %
    The first row {\bf C0} is the generator-level result and thus is common
    to all three categories.
    %
    \label{table:cutflow}
  }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The results for the three categories have been collected in
Table~\ref{table:cutflow}.
%
Let us begin with the discussion of the boosted category, the one that
leads to a higher signal significance.
%
We see that after all the cuts, including $b$-tagging,
we end up with almost 200 signal events at the HL-LHC, with
still a substantial background of around $40k$ events.
%
The signal significance is around 1.0 at the end of the
cut-based analysis.
%
While it should have been possible to increase this significance
but using more aggressive cuts, we have refrained doing so
since we prefer this optimisation to be performed at the level of
the MVA.

From the results of Table~\ref{table:cutflow}
it is possible to compute the corresponding numbers
for the end of Run II at the LHC with
$\mathcal{L}_{\rm int}=300$ fb$^{-1}$: in the boosted category,
we have only
19 signal events, and the signal significance drops down to
$S/\sqrt{B}\sim 0.3$.
%
We will discuss in the next section what are the Run II prospects
once we include the effects of the MVA in the analysis, but
it is clear already at this level that one really needs the full
integrated luminosity of the HL-LHC to be able to observe
the Higgs pair production process, unless  of course production rates are
increased by new BSM dynamics

@@

From the results of Table~\ref{table:cutflow}
we see that after the cut-based analysis, the significance of the Higgs pair production
observation in the $4b$ channel using the boosted topology
is $S/\sqrt{B}=0.99$,
and that the combination
of the boosted, intermediate and resolved categories gives a slightly higher
value, around 1.20.
%

@@

Since we find that the $2b2j$ and $4j$ backgrounds cannot
be neglected, and previous works did not considered them,
it is interesting to
study how our results are modified if we consider only the QCD $4b$
multi-jet background, but ignore the $2b2j$ and $4j$ backgrounds,
that is, we ignore the contribution from the fakes.
%
These results are shown in
Table~\ref{table:cutflow4B}, which is the analog of
Table~\ref{table:cutflow} but with only the QCD
$4b$ background taken into account.
%
As we can see, these results indicate that given the similarity of the final states
in signal and background events in these cases, the signal significance is
relatively stable at various stages of the cut-flow.
%
As compared to the case in which all backgrounds are taken into account, we
now get a factor two smaller backgrounds: we conclude that in the boosted category
the effect of the fakes is non-negligible, with their contribution being
comparable to that of the irreducible $4b$ QCD multi-jet background.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
  \centering
  \begin{tabular}{c|c|c||c|c||c|c}
    \hline
    \multicolumn{7}{c}{Boosted category}\\
    \hline
    \hline
    &    \multicolumn{2}{c||}{$\sigma$ (fb)}   &  \multicolumn{2}{c||}{$N_{\rm ev}$}
    &   $S/\sqrt{B}$  & $S/B$\\
      &    Signal & Back   &  Signal  & Back
    &   & \\
    \hline
        {\bf C0}  &  36.9  & $1.1\,10^{6}$ & $1.1\,10^5$ & $3.3\,10^{9}$  &  1.90 & $3.3\,10^{-5}$\\
        {\bf C1}  &  0.46    & $1.0\,10^2$    &  $1.4\,10^3$   & $3.1\,10^5$     & 2.48     &  $4.4\,10^{-3}$ \\
        {\bf C2}  &  0.064     &  7.1     &  193   &  $2.1\,10^4$    &  1.30    &  $9.1\,10^{-3}$ \\
        \hline
  \end{tabular}
   $\,$\\
  \vspace{0.4cm}
  \begin{tabular}{c|c|c|c|c|c|c}
    \hline
    \multicolumn{7}{c}{Intermediate category}\\
    \hline
    \hline
    &    \multicolumn{2}{c|}{$\sigma$ (fb)}   &  \multicolumn{2}{c|}{$N_{\rm ev}$}
    &   $S/\sqrt{B}$  & $S/B$\\
      &    Signal & Back   &  Signal  & Back
    &   & \\
    \hline
 {\bf C0}  &  36.9  & $1.1\,10^{6}$ & $1.1\,10^5$ & $3.3\,10^{9}$  &  1.90 & $3.3\,10^{-5}$\\
        {\bf C1}  &  0.46    & $7.2\,10^2$    &  $1.4\,10^3$   & $2.2\,10^6$     & 2.91     &  $1.9\,10^{-3}$ \\
        {\bf C2}  &  0.064     &  58.8     &  193   &  $1.8\,10^5$    &  1.57    &  $3.7\,10^{-3}$ \\
        \hline
  \end{tabular}
  $\,$\\
  \vspace{0.4cm}
  \noindent
  \begin{tabular}{c|c|c|c|c|c|c}
    \hline
    \multicolumn{7}{c}{Resolved category}\\
    \hline
    \hline
    &    \multicolumn{2}{c|}{$\sigma$ (fb)}   &  \multicolumn{2}{c|}{$N_{\rm ev}$}
    &   $S/\sqrt{B}$  & $S/B$\\
      &    Signal & Back   &  Signal  & Back
    &   & \\
    \hline
 {\bf C0}  &  36.9  & $1.1\,10^{6}$ & $1.1\,10^5$ & $3.3\,10^{9}$  &  1.90 & $3.3\,10^{-5}$\\
        {\bf C1}  &  0.46    & $9.0\,10^3$    &  $1.4\,10^3$   & $2.7\,10^7$     & 1.92     &  $3.7\,10^{-4}$ \\
        {\bf C2}  &  0.064     &  986     &  193   &  $2.9\,10^6$    &  0.95  &  $5.5\,10^{-4}$ \\
        \hline
  \end{tabular}
  \caption{\small Same as Table~\ref{table:cutflow}, but now
    only with the QCD $4b$ multi-jet background taken into account.
    %
    \label{table:cutflow4B}
  }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{Background decomposition}

Up to now we have considered the effects of all backgrounds added
together, except in Table~\ref{table:cutflow4B} and the corresponding
discussion where we have studies how our
results are modified if only the QCD $4b$ background is included.
%
In this section we study the decomposition of the background in each
of its individual components, for the three different categories
of events used in this work.
%

In Table~\ref{table:cutflowBack}   we show the results for the cross-sections for the different
backgrounds that we consider at the end of the cut-based analysis, for each
of the three categories.
%
Recall that all the backgrounds have been normalized to known higher-order results,
as summarized in Table~\ref{tab:samples}.
%
As we can see from this comparison, as opposed that what naively one would expect,
the QCD $2b2j$ background turns out not to be negligible as compared to the $4b$
multijets in any of the categories.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h]
  \centering
  \begin{tabular}{c|c|c|c}
    \hline
    Background  &    \multicolumn{3}{c}{$\sigma$ (fb)}   \\
    \hline
  &    Resolved  &  Intermediate  &   Boosted \\
    \hline
    \hline
  QCD $4b$   &   $9.9\,10^{2}$       &  $59$       &   $7.1$        \\
  QCD $2b2j$ &   $2.4\,10^{3}$       &  $6.4\,10^{2}$       &   $3.5$        \\
  QCD $4j$ &     $1.7\,10^{2}$       &   $22$      &    $2.1$        \\
  $t\bar{t}$ &   $3.6$       &  $2.2$       &   $4.5\,10^{-2}$        \\
  \hline
  \hline
Total     &    $3.6\,10^{3}$      &   $7.2\,10^{2}$      &     $13$      \\
\hline
\end{tabular}
    \caption{\small The cross-sections for each of the individual background
      components (and their total sum) at the end of the cut-based
      analysis, for each of three categories.
    \label{table:cutflowBack}
    }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In the boosted case, the sum of the $2b2j$ and $4j$ components is almost as large as the
irreducible $4b$ background, thus increasing the total background rates by a factor 2 as compared
to the case where only $4b$ is accounted for.
%
This effect is more dramatic in the intermediate and resolved categories: in the former,
$2b2j$ completely dominates the background (thus the increase in $S/\sqrt{B}$ noted in
Table~\ref{table:cutflow4B}  when only the $4b$ component is kept), and in the latter
it is comparable to $4b$.
%
Therefore, we conclude that an accurate estimate of the fake $b$-tag contribution is
an essential component of this analyses, and that complete QCD multijet samples
should be included.
%
On the other hand, we find that the hadronic $t\bar{t}$ component of the backround
is smaller than the QCD multijet one.

@@

  One might ask why the $2b2j$ process
  is not subdominant as compared to $4b$: while its generator-level cross-section is
  much larger, $\sigma_{2b2j} \simeq 240\sigma_{4b}$, one expects a suppression
  of the order of $f_l^2 =10^{-4}$ since only with two light jets mistagged as $b$-jets the event
  would be identified as a Higgs candidate.
  %
  We have checked that this expectation is true only at parton level: once parton shower effects
  are accounted for, both the radiation of $b\bar{b}$ pairs from the shower and combinatorics increase
  the number of $b$ quarks in the final state, enhancing substantially the $2b2j$ rates as compared
  to the naive parton level expectation.
  %
  To verify this, we plot the number of $b$-quarks.....

  {\bf compare parton level with hadron level distributions}

>>>>

\subsection{Cut-flow and signal significance}

First of all, we compare the cross-sections at various
analysis levels for the three categories, for signal and background events,
by providing a detailed cut-flow.
%
We consider all backgrounds enumerated in Sect.~\ref{mcgeneration},
and also discuss how results are modified if only the $4b$
component is kept.
%
At each stage of the cut-flow, we also provide the
the signal significance, $S/\sqrt{B}$, and the signal
over background ratio, $S/B$, for the case of the
 HL-LHC with
an integrated luminosity of $\mathcal{L}_{\rm int}
=3000$ fb$^{-1}$.
%
%
We emphasize that it is important not only to achieve a good signal
significance, $S/\sqrt{B}$, but also a good signal over background ratio $S/B$:
if the latter is too small, a very accurate
measurement of the background with an infeasible small
systematic uncertainty would be required.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
  \centering
  \begin{tabular}{|c|c|c|c|}
\hline
&  Boosted  &   Intermediate &  Resolved  \\
\hline
\hline
C0 &  Generator level &  Generator level & Generator level \\
\hline
C1a & $N_{\rm jets}^{R}\ge 2$ & $N_{\rm jets}^{r}\ge 2$, $N_{\rm jets}^{R}=1$  &
 $N_{\rm jets}^{r}\ge 4$ \\
 C1b & +$p_T$ cuts & +$p_T$ cuts
 & +$p_T$ cuts \\
 C1c & + rapidity cuts &  + rapidity cuts &
 + rapidity cuts \\
 C1d & + Mass-Drop tag required & $N_{\rm jets}^{R}=1$ with MDT  &
  Higgs reco possible \\
C1e & $m_H$ window cut & $m_H$ window cut & $m_H$ window cut  \\
\hline
C2 & $b$-tagging  &  $b$-tagging &  $b$-tagging \\
\hline
  \end{tabular}
  \caption{\small Details of the cut-flow of the present analysis in the boosted, intermediate
    and resolved categories.
    %
    See text for more details.
    \label{tab:cutflowdetails}
  }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

To begin with,
in Table~\ref{tab:cutflowdetails}
we summarize the details of the cut-flow of the present analysis,
separated into the exclusive boosted, intermediate
    and resolved categories.
    %
    From top to bottom, additional cuts are required in addition
    to the previous ones.
    %
    The various cuts
    are defined as follows
    \begin{itemize}
    \item {\bf C0}: these are the generator level cross-sections, with
      mild generation cuts in the case of the background processes.
    \item {\bf C1a}: at this level, we only check that we have at least
      two large-$R$ jets (in the boosted case),
      one large-$R$ jet and at least 2 small-$R$ jets (in the intermediate
      case) and at least four small-$R$ jets (in the resolved case).
      %
      No acceptance requirements are imposed here.
    \item {\bf C1b}: Same as C1a, but now the jets should
      satisfy the corresponding $p_T$ thresholds:
      $p_T \ge 200$ GeV for large-$R$ jets,
      $p_T \ge 50$ GeV for small-$R$ jets.
    \item {\bf C1c}: in addition, the above jets must satisfy the
      rapidity acceptance requirement.
    \item {\bf C1d}: at this level, large-$R$ jets must satisfy the
      mass-drop tag condition.
    \item {\bf C1e}: after the two Higgs candidate jets have been reconstructed,
      their invariant masses are required to lie within the
      $m_H$ window, namely
    \item {\bf C2}: finally, this is the level of the analysis
      after $b$-tagging has been performed.
      \end{itemize}
    Signal and background events that survive the C2 level cuts
    are then used as input for the MVA training, as described
    in Sect.~\ref{sec:mva}.

    %
    In Table~\ref{tab:cutflow_noPU_1} we provide
    the values of cross-sections in fb
     for the signal
      and the various background
      components as a function of the
      cut-flow, for the resolved,
      boosted and intermediate
      categories.
      %
      We see that although of course
      $b$-tagging suppressed very substantially the $2b2j$ and
      $4j$ backgrounds, it does not completely
      eliminate them.

\begin{table}[t]
  \centering
  \scriptsize
  \input{tables/table_noPU_1.tex}
  $\,$ \\
  \vspace{0.5cm}
  \input{tables/table_noPU_2.tex}
  $\,$ \\
  \vspace{0.5cm}
    \input{tables/table_noPU_3.tex}
    \caption{\small The cross-sections, in pb,
      for the signal and the various background
      processes at different points of the
      cut-flow, for the resolved (upper table),
      intermediate (middle table) and boosted
      (lower table) categories, for the analysis
      without PU.
      %
      In each case, we also provide the signal over
      background ratio, $S/B$, and the signal
      significance, $S/\sqrt{B}$, considering either
      the total background or only the $4b$ component.
 \label{tab:cutflow_noPU_1}}
\end{table}

%
Let us begin with the discussion of the boosted category, the one that
leads to a higher signal significance.
%
We see that after all the cuts, including $b$-tagging,
we end up with almost 200 signal events at the HL-LHC, with
still a substantial background of around $40k$ events.
%
The signal significance is around 1.0 at the end of the
cut-based analysis.
%
While it should have been possible to increase this significance
but using more aggressive cuts, we have refrained doing so
since we prefer this optimisation to be performed at the level of
the MVA.

From the results of Table~\ref{tab:cutflow_noPU_1}
it is possible to compute the corresponding numbers
for the end of Run II at the LHC with
$\mathcal{L}_{\rm int}=300$ fb$^{-1}$: in the boosted category,
we have only
19 signal events, and the signal significance drops down to
$S/\sqrt{B}\sim 0.3$.
%
We will discuss in the next section what are the Run II prospects
once we include the effects of the MVA in the analysis, but
it is clear already at this level that one really needs the full
integrated luminosity of the HL-LHC to be able to observe
the Higgs pair production process, unless  of course production rates are
increased by new BSM dynamics

@@

We observe
that after the cut-based analysis, the significance of the Higgs pair production
observation in the $b\bar{b}b\bar{b}$ channel using the boosted topology
is $S/\sqrt{B}=0.99$,
and that the combination
of the boosted, intermediate and resolved categories gives a slightly higher
value, around 1.20.
%

@@

Since we find that the $2b2j$ and $4j$ backgrounds cannot
be neglected, and previous works did not considered them,
it is interesting to
study how our results are modified if we consider only the QCD $4b$
multi-jet background, but ignore the $2b2j$ and $4j$ backgrounds,
that is, we ignore the contribution from the fakes.
%
As we can seen before in Table~\ref{tab:cutflow_noPU_1},
these results indicate that given the similarity of the final states
in signal and background events in these cases, the signal significance is
relatively stable at various stages of the cut-flow.
%
As compared to the case in which all backgrounds are taken into account, we
now get a factor two smaller backgrounds: we conclude that in the boosted category
the effect of the fakes is non-negligible, with their contribution being
comparable to that of the irreducible $4b$ QCD multi-jet background.

@@

@@

In Table~\ref{tab:cutflow_noPU_1}   we show the results for the cross-sections for the different
backgrounds that we consider at the end of the cut-based analysis, for each
of the three categories.
%
Recall that all the backgrounds have been normalized to known higher-order results,
as summarized in Table~\ref{tab:samples}.
%
As we can see from this comparison, as opposed that what naively one would expect,
the QCD $2b2j$ background turns out not to be negligible as compared to the $4b$
multijets in any of the categories.

In the boosted case, the sum of the $2b2j$ and $4j$ components is almost as large as the
irreducible $4b$ background, thus increasing the total background rates by a factor 2 as compared
to the case where only $4b$ is accounted for.
%
This effect is more dramatic in the intermediate and resolved categories: in the former,
$2b2j$ completely dominates the background (thus the increase in $S/\sqrt{B}$
obtained when only the $4b$ component is kept), and in the latter
it is comparable to $4b$.
%
Therefore, we conclude that an accurate estimate of the fake $b$-tag contribution is
an essential component of this analyses, and that complete QCD multijet samples
should be included.
%
On the other hand, we find that the hadronic $t\bar{t}$ component of the background
is smaller than the QCD multijet one.

@@

  One might ask why the $2b2j$ process
  is not subdominant as compared to $4b$: while its generator-level cross-section is
  much larger, $\sigma_{2b2j} \simeq 240\cdot \sigma_{4b}$, one expects a suppression
  of the order of $f_l^2 =10^{-4}$ since only with two light jets mistagged as $b$-jets the event
  would be identified as a Higgs candidate.
  %
  We have checked that this expectation is true only at parton level: once parton shower effects
  are accounted for, both the radiation of $b\bar{b}$ pairs from the shower and combinatorics increase
  the number of $b$ quarks in the final state, enhancing substantially the $2b2j$ rates as compared
  to the naive parton level expectation.
  %

  In the section section we show how Multivariate Analysis can be used
  to substantially improve the signal significance obtained in the
  cut-based analysis.
